Measuring Perceptions and Preferences for Meritocracy

### 2021-07-02 paper_study1.Rmd
ajuste bins

size=1.1
ggplot2::theme_set(ggplot2::theme(panel.background = ggplot2::element_rect(fill = "gray85",
                                                                           colour = "gray85"),
                                  panel.border = ggplot2::element_blank(),
                                  axis.text.y = ggplot2::element_text(size = 12,
                                                                      hjust = 1),
                                  title = ggplot2::element_text(size = 12,
                                                                face = "bold"),
                                  legend.text = ggplot2::element_text(size = 12),
                                  plot.caption = ggplot2::element_text(size = 10,
                                                                       face = "plain",
                                                                       hjust = 1)))
p1<- likert_issp %>%
  dplyr::select(hwork_r:ambition_r) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Perception meritocratic",
                        geom.size = c(0.6*size),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE) + 
  ggplot2::theme(legend.position = "none")

p2<-likert_issp %>%
  dplyr::select(wealthy_r:polcone_r) %>% 
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Perception Non-meritocratic",
                        geom.size = c(0.78*size),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE)  + 
  ggplot2::theme(legend.position = "none")

p3<-likert_issp %>% 
  dplyr::select(welljob_r:hardjob_r) %>% 
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Preference meritocratic",
                        geom.size = c(0.6*size),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE) + 
  ggplot2::theme(legend.position = "none")

p4<-likert_issp %>% 
  dplyr::select(family_r:child_r) %>% 
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Preference Non-meritocratic",
                        geom.size = c(0.6*size),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = F,
                        reverse.scale = F,
                        show.n = FALSE) +
  ggplot2::labs(caption = paste0("n=",dim(likert_issp)[1]))+
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::scale_fill_brewer(breaks=c(5:1),
                             direction = -1,
                             labels = c("Not important at all","Not very important",
                                        "Fairly important","Very important","Essential"))
```

```{r likert-issp,fig.height=10,fig.width=12,fig.cap="Distribution of responses in the ISSP meritocracy items"}
# plot_likert_issp
cowplot::plot_grid(p1,p2,p3,p4,
                     align = "hv", 
                     axis = "a",
                     nrow = 4, 
                     ncol = 1,
                     rel_heights = c(1,2,1,1.3))
```

>>>>

ggplot2::theme_set(ggplot2::theme(panel.background = ggplot2::element_rect(fill = "gray85",
                                                                           colour = "gray85"),
                                  panel.border = ggplot2::element_blank(),
                                  axis.text.y = ggplot2::element_text(size = 12,
                                                                      hjust = 1),
                                  title = ggplot2::element_text(size = 12,
                                                                face = "bold"),
                                  legend.text = ggplot2::element_text(size = 12),
                                  plot.caption = ggplot2::element_text(size = 10,
                                                                       face = "plain",
                                                                       hjust = 1)))
p1<- likert_issp %>%
  dplyr::select(hwork_r:ambition_r) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Perception meritocratic",
                        geom.size = c(0.62),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE) + 
  ggplot2::theme(legend.position = "none")

p2<-likert_issp %>%
  dplyr::select(wealthy_r:polcone_r) %>% 
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Perception Non-meritocratic",
                        geom.size = c(0.9),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE)  + 
  ggplot2::theme(legend.position = "none")

p3<-likert_issp %>% 
  dplyr::select(welljob_r:hardjob_r) %>% 
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Preference meritocratic",
                        geom.size = c(0.62),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE) + 
  ggplot2::theme(legend.position = "none")

p4<-likert_issp %>% 
  dplyr::select(family_r:child_r) %>% 
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Preference Non-meritocratic",
                        geom.size = c(0.62),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = F,
                        reverse.scale = F,
                        show.n = FALSE) +
  ggplot2::theme(legend.position = "none")

leg<- ggpubr::as_ggplot(
  ggpubr::get_legend(
    dplyr::select(likert_issp, family_r:child_r) %>%
      sjPlot::plot_likert(geom.colors = "PuBu", catcount = 5) +
      ggplot2::scale_fill_brewer(
        breaks = c(5:1),
        direction = -1,
        labels = c("Not important at all","Not very important","Fairly important",
                   "Very important","Essential")) +
      ggplot2::theme(legend.position = "bottom")
    )
  )
```

```{r likert-issp,fig.height=10,fig.width=12,fig.cap="Distribution of responses in the ISSP meritocracy items"}
cowplot::add_sub(
  cowplot::plot_grid(p1,p2,p3,p4,leg,
    align = "hv",
    axis = "a",
    nrow = 5,
    ncol = 1,
    rel_heights = c(1,2,1,1,0.25)
    ),
  label = paste0(
    "Source: Authors calculation based on International Social Survey Programme - Social Inequality 2009",
    " (n=",dim(likert_issp)[1],")"
    ),
  size = 10,
  hjust = 0.15
  ) %>% 
  cowplot::ggdraw() 
```
